Response to the defense feedback

### 2021-05-30 Chapter-5/Chapter-5.tex
Updates from Overleaf

Considering the example in figure~\ref{fig:align}, it read data from the array \textsf{T} based on the index ($i$). If secret can affect the value of index ($i$), it could be a side-channel vulnerability. Unlike the example in the previous section, the array \textsf{T} is on the heap. Data on the heap are allocated at different addresses each time. Suppose during the first run, \textsf{T} is allocated at the address \textsf{0xff124800} and \textsf{T} is allocated at the address \textsf{0xff124801} at the second run. For the example in Figure~\ref{fig:align}(a), the index that is used to access the array is always $1$, so it should not be a side-channel vulnerability here, however, because the based address is different. So we get two different memory accesses. Under the circumstance, it is a false positive. Besides, it can cause false negatives, as the example shown in Figure~\ref{fig:align}(b). In the example, different keys lead to different indexes. However, as $T_0 + i_0$ equals to $T_1 + i_0$, \ctool{} can not observe the difference here, which can cause a false positive.

>>>>

Considering the example in figure~\ref{fig:align}, it read data from the array \textsf{T} based on the index ($i$). If secret can affect the value of index ($i$), it could be a side-channel vulnerability. Unlike the example in the previous section, the array \textsf{T} is on the heap. Data on the heap are allocated at different addresses each time. Suppose during the first run, \textsf{T} is allocated at the address \texttt{0xff124800} and \textsf{T} is allocated at the address \texttt{0xff124801} at the second run. For the example in Figure~\ref{fig:align}(a), the index that is used to access the array is always $1$, so it should not be a side-channel vulnerability here, however, because the based address is different. So we get two different memory accesses. Under the circumstance, it is a false positive. Besides, it can cause false negatives, as the example shown in Figure~\ref{fig:align}(b). In the example, different keys lead to different indexes. However, as $T_0 + i_0$ equals to $T_1 + i_0$, \ctool{} can not observe the difference here, which can cause a false positive.
